%-------------------------
% Resume in Latex
% Author : Vaishanth
% License : MIT
%------------------------

\documentclass[letterpaper,10.5pt,]{article}
\renewcommand{\baselinestretch}{1.2} 

\usepackage{amsmath}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}%\setmainfont{Times New Roman}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% \usepackage[T1]{fontenc}
% \usepackage[T1]{fontenc}
% \usepackage{cochineal}
% \usepackage{fourier}

% \usepackage{fontspec}
% \usepackage{polyglossia}
% \setmainlanguage{german}
% \setmainfont{Times New Roman}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.55in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSingleSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------\usepackage{fontspec}
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------


\begin{center}
    {\huge Yufeng(Felix) Xu} \\ \vspace{2pt} 
    {+86 15151521422} ~ 
    \small{-}
    %\href{[url to portfolio]}{\color{blue}{Portfolio}} ~ 
    %\small{-}
    \href{mailto:yx3038@nyu.edu}{\color{airforceblue}{yx3038@gmail.com}} ~ 
    \small{-}
    \href{https://www.linkedin.com/in/yufeng-felix-xu/}{ \color{airforceblue}{linkedin.com/in/yufeng-felix-xu}}  ~
    \small{-}
    \href{https://github.com/Zephyr271828}{ \color{airforceblue}{github.com/Zephyr271828}} ~
    \vspace{-7pt}
\end{center}

%-----------EDUCATION-----------
\section{\color{airforceblue}EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New York University Shanghai}{567 West Yangsi Road, Pudong New District, Shanghai, China}
      {Computer Science}{Sep 2022 - Jun 2026}
      \resumeItemListStart
          \resumeItem{\normalsize{\textbf{Cumulative GPA:} 4.0/4.0 (Top 1/500)}}
          \resumeItem{\normalsize{\textbf{Honors and Scholarships:} Lizhong Scholarship (\textbf{full scholarship} upon admission)}}
          \resumeItem{\normalsize{\textbf{Relevant Coursework:}}}
          \vspace{-5pt}
          \begin{flalign*}
          &\ast\text{Machine Learning}&&\ast\text{Computer Vision}&&\ast\text{Natural Language Processing}&\\
          &\ast\text{Algorithms(99.0)}&&\ast\text{Data Structures(97.4)}&&\ast\text{Probability \& Statistics(99.6)}&\\
          &\ast\text{Discrete Mathematics(99.1)}&&\ast\text{Linear Algebra(98.6)}&&\ast\text{Multivariate Calculus(99.7)}&
          \end{flalign*}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
  \vspace{-20pt}

%-----------Publications---------------
\section{\color{airforceblue}PUBLICATIONS}
    
  \resumeItemListStart
    \resumeItem{\normalsize{L. Guo, K. Ross, Z. Zhao, G. Andriopoulos, S. Ling, \textbf{Y. Xu,} and Z. Dong. \textit{Cross Entropy versus Label Smoothing: A Neural Collapse Perspective,} Feb 2024.  
Submitted to NeuRIPS 2024.}}\href{https://arxiv.org/abs/2402.03979}{\color{airforceblue}\underline{Arxiv}}
    \vspace{-5pt}

    % copy and paste above resumeItem block to add more 
    
  \resumeItemListEnd 
      
\vspace{-8pt}
 
 %-----------EXPERIENCE-----------
\section{\color{airforceblue}RESEARCH EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Neural Collapse under the setting of Label Smoothing}{Jun 2023 - Feb 2024}
      {Supervised by: Prof. Keith Ross, Prof. Li Guo}{NYU Shanghai, Shanghai, China}
      \vspace{-.5pt}
      \resumeItemListStart
            \resumeItem{\normalsize{Investigated the Neural Collapse Phenomenon in terminal phase of training to explain the essence of deep learning.}}
            \resumeItem{\normalsize{Looked into Neural Collapse under Cross Entropy and Label Smoothing loss, proved that NC is more prevalent under LS loss in both theory and practice.}} 
            \resumeItem{\normalsize{Integrated Distributed Data Parallel to our experiment codes and improved the efficiency of training significantly.}}   
      \resumeItemListEnd  

    \resumeSubheading
      {Bidirectional Diffusion Model}{Feb 2024 - Now}
      {Supervised by: Prof. Tianyi Zhou, Prof. Shengjie Wang}{NYU Shanghai, China}
      \vspace{-.5pt}
      \resumeItemListStart
            \resumeItem{\normalsize{Designing a novel bidrectional architecture for diffusion model to incorporate both text and image data and perform text-to-image, image-to-image, image-to-text, text-to-text and other downstream tasks.}}
            \resumeItem{\normalsize{Apply a new noise schedule strategy to realize fine-grained control of the equilibrium of information entropy to balance the weights of different modalities. }}
      \resumeItemListEnd  

    \resumeSubheading
      {A*esque Neurologic Decoding Algorithm \& Tool LLMs}{Feb 2024 - Now}
      {Supervised by: Prof. Chen Zhao}{NYU Shanghai, China}
      \vspace{-.5pt}
      \resumeItemListStart
            \resumeItem{\normalsize{Conducting a empirical comparison study between tool LLMs and constrained decoding algorithms to investigate which method mitigates the hallucination of language models better. }}
      \resumeItemListEnd  

    % copy and paste above resumeSubheading block to add more 
  \resumeSubHeadingListEnd
\vspace{-17pt}


 %-----------PROJECTS-----------
\section{\color{airforceblue}PROJECTS}    
    \resumeSubHeadingListStart

    \resumeSubheading
      {LLM-powered Dating Application
      \href{https://github.com/screenl/amireux_beta}{\color{airforceblue}\underline{GitHub}}}{} 
      {Digital Innovation Challenge, NYU Shanghai}{Nov 2023}
      \vspace{-.5pt}
      \resumeItemListStart
            \resumeItem{\normalsize{Created an LLM-powered dating app – Amireux – to provide tailored chatbot service for users, learn users’ traits, and match users effectively. Prompt-engineered the GPT-4 model to make AI chat in a more human-like way and adapt according to users’ response.}}
            \resumeItem{\normalsize{Obtained Top 10 ranking among 80+ teams in the NYU Shanghai Digital Innovation Challenge; launched a beta test in NYU Shanghai involving 10+ students and highly regarded by the users.}}
      \resumeItemListEnd  
    \resumeSubHeadingListEnd

        % copy and paste above resumeItem block to add more 
        
   
 \vspace{-17pt}
%

%-----------PROGRAMMING SKILLS-----------
\section{\color{airforceblue}TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{\normalsize{Programming Languages:}}{ \normalsize{Python, C++, LaTeX, Matlab, SQL, Shell}} \\
      \vspace{1.2pt}
      
     \textbf{\normalsize{Libraries and Tools:}}{ \normalsize{PyTorch,  Sklearn, Pandas, Numpy, Flask, Git, HPC}} \\
      \vspace{1.2pt}

     % copy and paste above textbf block to add more 
     }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXTRACURRICULAR---------------
\section{\color{airforceblue}EXTRACURRICULAR ACTIVITIES}
    \textbf{Vice President} of NYU Shanghai ACM Chapter \hfill \textit{\small Dec 2023 - June 2024} 
    \textbf{Leader} of NYU Shanghai AI Interest Group  \hfill \textit{\small June 2023 - Now} 
\end{document}
